---
title: "day five comp"
author: "Allie Cole"
date: "8/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Taking a look at `starwars` 

- `include=` to show or hide everything
- `echo=` to show to hide code 
- `warning=` to hide warnings 
- `eval=` to hide the output but show the code

```{r, include=FALSE}

# summary of data 
summary(starwars)

# getting the dimentions 
dim(starwars)
```

```{r, warning=FALSE}
ggplot(data = starwars, aes(x = height, y = mass)) +
  geom_point(color = "purple")
```

### find mean, variance, sd of character height 

```{r}
# sw_height_mean <- mean(starwars$height) won't work because it has NAs, so we add in the na.rm

sw_height_mean <- mean(starwars$height, na.rm = TRUE) 
# units are cm

sw_height_var <- var(starwars$height, na.rm = TRUE) 
# and the units are cm^2

sw_height_sd <- sd(starwars$height, na.rm = TRUE)
# the units are cm 
```

Mean character height is `r round(sw_height_mean, 0)` cm, with a standard devation of `r round(sw_height_sd, 1)` cm

### Logical Expressions 

#### comparison operators 
```{r}
5 < 10 

"cats" > "ant" #will do alphabetical

10 <= 11

4 >= 3

# play around with vectors 

tarantulas <- c(1, 3, 7, 15)

tarantulas > 5 # returns a vector of same length 

```

#### logical operators 

- `!` not 
- `&` and 
- `|`or 

```{r}
3 < 1 | 8 > 2

6 < 10 & 5 < 1 

7 != 11 

4 != 4 | 2 < 5 | 6 > 10 

0 == FALSE 

1 == TRUE 
```






















